The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-04 paper/main.tex
paper: improve discussion

The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
is the number of unresolved point-sources on sky, $N_{\rm s,a}$.
Assuming that the apparent stellar radius is fixed, then given the 
apparent planet radius $r\a$,
\begin{equation}
N_{\rm s,a}(r\a) = N\s^0(r\a) \times (1 + \mu)
\label{eq:apparentlysearchable_to_searchable}
\end{equation}
relates the number of apparently searchable point-sources to the number of 
searchable singles.
From the discussion above, it should be clear that there are in fact
$N\s^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
observers are under-counting.

@@

To check whether non-twin binaries change the above result, we now assume 
$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
This changes $\mu$ (Eq.~\ref{eq:mu_general} simplifies to 
Eq.~\ref{eq:mu_power_laws}).
It may also affect the rate density, which could be a function of the 
(varying) stellar mass.
Absorbing this dependence into a power law as well,
\begin{equation}
\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
\frac{M^\gamma}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry 
the units (each side has units $[r^{-1} M^{-1}]$).
We assume that stars are a one-parameter family, given by $R \propto M \propto 
L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
about a secondary.

@@

In short, the answer to our question is ``it depends on the number of planets 
orbiting secondaries, and also on the apparent radius of the detected planet''.
In the scenario that high-resolution imaging finds a system with $r\a > 
2r_\oplus$ in a binary, roughly $\sim 2.5\times$ more detected planets orbit 
primaries than secondaries, for the $Z_2/Z_0=1$ case.
For the $Z_2/Z_0=0.5$ case, $\sim 5\times$ more detected 
planets orbit primaries than secondaries.
So, relative to the cutoff in the intrinsic rate density, detected planets in 
binaries with large apparent radii are more likely to orbit the primary.

@@

\paragraph{How has binarity been considered in occurrence rate measurements?}
This study has shown that under a reasonable set of simplifying assumptions, 
ignoring binarity introduces systematic errors to star and planet counts in 
transit surveys, which then bias derived occurrence rates.
Thus far, real-world occurrence rate calculations\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
} using transit survey data have mostly ignored stellar 
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, 
it seems that no one has yet carefully assessed binarity's importance, or lack 
thereof.
While we do not resolve the problem, we do suggest the approximate scale of 
the possible errors in a survey-independent manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

This high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; 
\citealt{petigura_CKS_2017}).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true number of searchable stars, and thus the true 
occurrence rates, will remain biased.

\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
To interpret whether the results of this study are of any help for removing 
binarity's effects from the {\it Kepler}\ planet sample, a few practical 
concerns become pressing.

@@

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In the power law model of Sec.~\ref{sec:model_3}, we noted that the inferred 
rate can be up to 50\% higher than the true rate around single stars.
Though this bias seems large, it is currently small compared to the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If a future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

One relevant caveat to our assessment of binarity's importance for 
$\eta_\oplus$ measurements is that none of our models 
included the rate density's period-dependence. However, close binaries usually
provoke dynamical instabilities, leading to fewer long-period planets per 
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
    kraus_impact_2016}.
This effect might further affect transit survey measurements of $\eta_\oplus$
beyond our rough estimate.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity has been suggested as 
a possible source of discrepant occurrence rate measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
[{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
0.7$, and noted that this would imply that the metallicity difference could 
account for a $\approx 20\%$ relative difference in the measured rates between 
the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
\citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
This gives an $\approx 25\%$ relative difference, indicating metallicity could 
account for about half of the ``hot Jupiter rate discrepancy''.
}.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

Aside from surveying stars of varying metallicities, radial velocity and 
transit surveys differ in how they treat binarity.
Radial velocity surveys typically reject both visual and spectroscopic binaries
\citep[\textit{e.g.},][]{wright_frequency_2012}.
Transit surveys typically observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a bias against confirmation of 
transiting planets in binary systems.

Ignoring these complications, in this work we showed that
binarity biases transit survey occurrence rates through its effects on 
star counts and the apparent radii of detected planets.
Our results from Sec.~\ref{sec:model_3} indicate that binarity 
could lead to underestimated HJ rates relative to singles by a multiplicative 
factor of at most $\approx 1.13$ (assuming a power-law radius distribution, 
and that no secondaries host HJs).
We later pointed out in Sec.~\ref{sec:further_models} that assuming a 
power-law radius distribution is probably wrong if one wishes to study the HJ 
rate discrepancy. If we instead assumed a 
Gaussian radius distribution~\citep[following][]{petigura_CKS_2017}, apparent 
HJ rates are actually {\it greater} 
than the true rate around singles.
\begin{comment}
If we believe the assumed power-law radius distribution, we can ask whether 
this ``correction factor'' might help resolve the discrepancy.
Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
suggesting a weak discrepancy.

This suggestion should be taken with caution, because it (likely incorrectly) 
assumes a power-law radius distribution.
\end{comment}
This means that assuming a Gaussian similar to that reported 
by~\citet{petigura_CKS_2017}, binarity is unlikely to resolve the HJ rate 
discrepancy.
Of course, such calculations can be at most suggestive~--~a true resolution 
of binarity's effects may require a detailed understanding of the 
{\it Kepler}\ field's multiplicity statistics, and the mission's completeness 
(both for candidate detection and follow-up).
For instance, if hot Jupiters are less likely to be confirmed in binary 
systems, this might bias the rates low.

\paragraph{Fraction of detected planets with binary companions vs. apparent 
radius}
A prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of detected 
planets with binary companions increases by $\approx 6-12\%$ going from 
$2r_\oplus$ to $\approx 1.4r_\oplus$.
In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
they reported the fraction of planet-hosting stars with Robo-AO detected 
companion stars, binning by Earths ($r\a < 1.6r_\oplus$), Neptunes 
($1.6r_\oplus < r\a < 3.9 r_\oplus$), Saturns ($3.9r_\oplus < r\a < 9 
r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
The reported nearby star rates and their $1\sigma$ uncertainties are:
\begin{itemize}
    \item Earths: $16.3 \pm 1.0\%$, from 1480 systems.
    \item Neptunes: $13.0 \pm 0.8\%$, from 2058 systems.
    \item Saturns: $13.6 \pm 2.0\%$, from 338 systems.
    \item Jupiters: $19.0 \pm 2.8\%$, from 247 systems.
\end{itemize} 
where the uncertainties were calculated 
following~\citet{burgasser_binarity_2003}.
The absolute values of the rates are less than the $\sim 45\%$ typical for 
Sun-like stars at least in part because of Robo-AO's sensitivity 
(\citealt{ziegler_robo-ao_2017}'s Fig.~2;~\citealt{raghavan_survey_2010}).
Another reason for the lower measured companion rates could be that planetary 
systems are less likely to have 
binary companions (as~\citealt{kraus_impact_2016} argued for close binary 
companions).
The uptick in the companion rate for Jupiters is likely tied to a large 
astrophysical false positive rate~\citep{santerne_sophie_2012}.
Going from Neptunes to Earths, the data suggest a weak increase in the 
detected planet companion fraction, perhaps of a few percent.

\paragraph{Does a detected planet orbit the primary or secondary?}
\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
on the planet radii derived from transit surveys.
They modeled the problem for {\it Kepler}\ objects of interest by matching a 
population of binary and tertiary companions to KOI stars, 
under the assumption that the KIC-listed stars were the primaries.
They then computed planet radius correction factors assuming that {\it 
    Kepler}-detected planets orbited the primary or companion stars
with equal probability (their Sec.~5).
Under these assumptions, they found that any given planet's radius is on 
average underestimated by a multiplicative factor of $\approx\! 1.5$.
\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
correction factor for the multiple systems observed by the Robo-AO KOI survey, 
using the same assumption that detected planets are as likely to orbit the 
primary and the secondary.

Assuming a broken power-law radius distribution, we showed in 
Fig.~\ref{fig:frac_model_3} that assuming a detected planet has equal 
probability of orbiting the primary or secondary probably is rarely correct.
A planet orbiting the secondary does lead to extreme corrections.
However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
$Z_2/Z_0$ assumed in Fig.~\ref{fig:frac_model_3}, a detected planet is always 
more likely to orbit the primary than the secondary.
Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
secondaries host as many planets as singles and primaries, does this norm 
break down.

Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
might not apply to the {\it Kepler}\ dataset.
If they do, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
\url{exoplanetarchive.ipac.caltech.edu}} with 
apparent radii $>2r_\oplus$, 
whenever high-resolution imaging 
discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

\paragraph{Utility in future occurrence rate measurements}
{\it TESS}\ is expected to discover over $10^4$ giant 
planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
Though they will be difficult to distinguish from false positives, one 
possible use of this large sample will to measure an occurrence rate of 
short-period giant planets with minimal error from counting statistics.
Our models suggest that binarity will only become an appreciable fraction of 
the error budget at the $\approx 10\%$ precision level.
This should be sufficient for a rate measurement precise enough to indicate a 
preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
hot Jupiters.

@@

\newpage
\appendix
\section{Derivation of general formula for apparent occurrence rate}
\label{sec:appendix}
Recall our definition of apparent rate density 
(Eq.~\ref{eq:defn_apparent_rate_density}).
Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
determined from the assumed stellar mass--radius--luminosity relation. We 
neglect the dependence on planetary orbital period.
The planets with $(r\a, M\a)$ are associated with 
systems of many different planetary and stellar properties, so $n_{\rm 
det}(r\a, M\a)$ is given by the convolution of the true rate density, 
$\Gamma(r, M)$, and $\mathcal{N}(r\a, M\a; r, M)$, the number (per 
unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
the true system actually has $(r, M)$. Mathematically,
\begin{align}
n_{\rm det}(r_a, M_a) &=
\sum_i n_{\rm det}^i(r_a, M_a) \\
&=
\sum_i \int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
\cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
\label{eq:n_det}
\end{align}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
secondary).
The problem reduces to the evaluation of
\begin{equation}
\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in 
binaries.

>>>>

The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
is the number of unresolved point-sources on sky that the observer thinks are 
searchable, $N_{\rm s,a}$.
Assuming that the apparent stellar radius is fixed, then given the 
apparent planet radius $r\a$,
\begin{equation}
N_{\rm s,a}(r\a) = N\s^0(r\a) \times (1 + \mu)
\label{eq:apparentlysearchable_to_searchable}
\end{equation}
relates the number of apparently searchable point-sources to the number of 
searchable singles.
From the discussion above, it should be clear that there are in fact
$N\s^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
observers are under-counting.

@@

To check whether non-twin binaries change the preceding result, we now assume 
$f(q) = q^\beta/\mathcal{N}_q$, for $\mathcal{N}_q$ the normalization.
This changes $\mu$ (Eq.~\ref{eq:mu_general} simplifies to 
Eq.~\ref{eq:mu_power_laws}).
It may also affect the rate density, which could be a function of the 
(varying) stellar mass.
Absorbing this dependence into a power law as well,
\begin{equation}
\Gamma_i(r,M) = Z_i \times \frac{r^\delta}{\mathcal{N}_r} \times
\frac{M^\gamma}{\mathcal{N}_M},
\end{equation}
where $Z_i$ is dimensionless, and the normalization constants carry 
the units (each side has units $[r^{-1} M^{-1}]$).
We assume that stars are a one-parameter family, given by $R \propto M \propto 
L^{\frac{1}{\alpha}}$, so that a given value of $q$ determines everything 
about a secondary.

@@

In short, the detected planet usually is more likely to orbit the primary, but 
it depends on the number of planets orbiting secondaries, and also on the 
apparent radius of the detected planet.
In the scenario that high-resolution imaging finds a system with $r\a > 
2r_\oplus$ in a binary, roughly $\sim\! 2.5\times$ more detected planets orbit 
primaries than secondaries, for the $Z_2/Z_0=1$ case.
For the $Z_2/Z_0=0.5$ case, $\sim\! 5\times$ more detected 
planets orbit primaries than secondaries.
So detected planets in binaries with large apparent radii (relative to the 
cutoff in the intrinsic rate density) are more likely to orbit the primary.

@@

\paragraph{How bad is ignoring binarity?}
This study has shown that under a reasonable set of simplifying assumptions, 
ignoring binarity introduces systematic errors to star and planet counts in 
transit surveys, which then biases derived occurrence rates.
Thus far, occurrence rate calculations\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
} using transit survey data have mostly ignored stellar 
multiplicity~\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, 
it seems that no one has yet carefully assessed binarity's importance, or lack 
thereof.
Although this study does not resolve the problem, it does suggest the 
approximate scale of the possible errors, in a survey-independent manner.
The suggestion of Sec.~\ref{sec:model_2} is that for $r\a \gtrsim 2r_\oplus$, 
binarity can be ignored down to the $\sim$few percent precision level.
For apparent radii $\lesssim 2r_\oplus$, the picture is less forgiving:
Sec.~\ref{sec:model_3} suggests that relative errors between apparent rates 
and true rates around singles could easily reach $\sim\! 50\%$.

\paragraph{The rate of Earth analogs}
In line with {\it Kepler}'s primary science goal, the rate of Earth-like 
planets orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts revealed that the one-year terrestrial planet occurrence rate 
is between $\approx\! 0.03$ and $\approx\!1$ per Sun-like star,
depending on assumptions that are made when calculating the rate 
(\citealt{burke_terrestrial_2015}'s Fig.~17).
In Sec.~\ref{sec:model_3}, our power law model indicates that when singles and 
secondaries host the same number of planets, the apparent rate is 50\% higher 
than the true rate around single stars.
Though this bias seems large, it is currently smaller than the other 
systematic factors that dominate the dispersion in $\eta_\oplus$ 
measurements.
If future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity will likely merit closer attention.

One caveat to this assessment of binarity's importance for 
$\eta_\oplus$ measurements is that none of our models 
included the rate density's period-dependence. However, close binaries usually
provoke dynamical instabilities, leading to fewer long-period planets per 
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
    kraus_impact_2016}.
This might affect transit survey measurements of $\eta_\oplus$ beyond our 
rough estimate.

\paragraph{Hot Jupiter rate discrepancy}
While binarity may appreciably affect $\eta_\oplus$ measurements, our analysis
suggests that it is unlikely to influence the hot Jupiter rate discrepancy.
The context of this disagreement is that hot Jupiter occurrence rates measured 
by transit surveys ($\approx 0.5\%$) are marginally lower than those found by 
radial velocity surveys ($\approx 1\%$; see Table~\ref{tab:hj_rates}).
Though the discrepancy has weak statistical significance ($<3\sigma$),
one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
Investigating the discrepancy from the metallicty 
angle,~\citet{guo_metallicity_2017} measured the
{\it Kepler} field's mean metallicity to be $[{\rm M/H}]_{\rm Kepler}= 
-0.045\pm0.009$, which is lower than the California Planet Search's mean of 
$[{\rm M/H}]_{\rm CPS}= -0.005\pm0.006$.
The former value agrees with that measured by \citet{dong_metallicities_2014}.
Refitting for the metallicity exponent in $\Lambda_{\rm HJ} \propto 10^{\beta 
    [{\rm M/H}] }$, \citeauthor{guo_metallicity_2017}\! found $\beta = 2.1\pm 
0.7$, and noted that this would imply that the metallicity difference could 
account for a $\approx 20\%$ relative difference in the measured rates between 
the CKS and {\it Kepler}\ samples~--~not a factor of two\footnote{
    \citet{petigura_CKS_2017} recently found $\beta = 3.4^{0.9}_{-0.8}$.
    This gives an $\approx 25\%$ relative difference, indicating metallicity 
    could 
    account for about half of the ``hot Jupiter rate discrepancy''.
}.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

The hypothesis that binarity might matter is grounded in the fact that radial 
velocity and transit surveys treat binarity differently.
Radial velocity surveys typically reject both visual and spectroscopic binaries
\citep[\textit{e.g.},][]{wright_frequency_2012}.
Transit surveys observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a tendency against confirming 
transiting planets in binary systems.

Ignoring these complications, in this work we concentrated on binarity's 
effects on star counts and the apparent radii of detected planets.
Assuming a power-law radius distribution, and that no secondaries host HJs,
our results from Sec.~\ref{sec:model_3} indicate that binarity 
could lead to underestimated HJ rates relative to singles by a multiplicative 
factor of at most $\approx 1.13$.
We later pointed out in Sec.~\ref{sec:further_models} that assuming a 
power-law radius distribution is probably wrong if one wishes to study the HJ 
rate discrepancy.
If we instead assumed a Gaussian radius 
distribution~\citep[following][]{petigura_CKS_2017}, apparent 
HJ rates are {\it greater} than the true rate around singles: the effect goes 
the wrong way.
\begin{comment}
If we believe the assumed power-law radius distribution, we can ask whether 
this ``correction factor'' might help resolve the discrepancy.
Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
suggesting a weak discrepancy.

This suggestion should be taken with caution, because it (likely incorrectly) 
assumes a power-law radius distribution.
\end{comment}
The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017} cannot 
possibly be part of a continuous power law. 
Thus binarity is unlikely to resolve the HJ rate discrepancy.

Of course, such calculations are only suggestive; a conclusive resolution 
of binarity's effects may require a detailed understanding of the 
{\it Kepler}\ field's multiplicity statistics, and the mission's completeness 
(both for candidate detection and follow-up).
For instance, if hot Jupiters are less likely to be confirmed in binary 
systems, this might bias the rates low.
Alternatively, {\it TESS}\ is expected to discover over $10^4$ 
giant planets~\citep{ricker_transiting_2014,sullivan_transiting_2015}.
Though they will be difficult to distinguish from false positives, one 
possible use of this sample will to measure an occurrence rate of 
short-period giant planets with minimal error from counting statistics.
Our models suggest that binarity will only become an appreciable fraction of 
the error budget at the $\approx 10\%$ precision level.
This should be sufficient for a rate measurement precise enough to indicate a 
preference between $\approx 0.5\%$ and $\approx 1\%$ of Sun-like stars hosting 
hot Jupiters.

\paragraph{Practical effects: smooth detection efficiencies; finite SNR floors}
To relate this study's results to {\it Kepler}\ and other transit surveys, a 
few practical concerns become pressing.

@@

\paragraph{Connecting high resolution imaging to occurrence rates}
A direct reason to address stellar multiplicity in transit surveys is that it 
changes the interpretation of planet candidates on a system-by-system level.
Consequently, high resolution imaging 
campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

These high resolution imaging campaigns are also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; 
\citealt{petigura_CKS_2017}).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true number of searchable stars, and thus the true 
occurrence rates, will remain biased.

\paragraph{Does a detected planet orbit the primary or secondary?}
One important step towards rectifying binarity's effects is identifying the 
host star for any detected planets in binaries.
The current 
wisdom is that nothing substantive can be said about the 
likelihood of a planet orbiting the primary vs. the 
secondary~\citep[\textit{e.g.},][]{ciardi_understanding_2015,ziegler_robo-ao_2017}.
This of course ignores cases when planets can be confirmed to orbit either 
component by analyzing the transit durations or centroids.

\begin{comment}
\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
on the planet radii derived from transit surveys.
They modeled the problem for {\it Kepler}\ objects of interest by matching a 
population of binary and tertiary companions to KOI stars, 
under the assumption that the KIC-listed stars were the primaries.
They then computed planet radius correction factors assuming that {\it 
    Kepler}-detected planets orbited the primary or companion stars
with equal probability (their Sec.~5).
Under these assumptions, they found that any given planet's radius is on 
average underestimated by a multiplicative factor of $\approx\! 1.5$.
\citet{ziegler_robo-ao_2017} recently reported a similar mean radius 
correction factor for the multiple systems observed by the Robo-AO KOI survey, 
using the same assumption that detected planets are as likely to orbit the 
primary and the secondary.
\end{comment}

Assuming a broken power-law radius distribution, we showed in 
Fig.~\ref{fig:frac_model_3} that there are many cases where a detected planet 
is much more likely to orbit the primary.
A planet orbiting the secondary does lead to extreme corrections.
However, at $r\a \gtrsim 2r_\oplus$, these cases are rare outliers.
At $r_\oplus \lesssim r\a \lesssim 2r_\oplus$, for all of the trial values of 
$Z_2/Z_0$ assumed in Fig.~\ref{fig:frac_model_3}, a detected planet is always 
more likely to orbit the primary than the secondary.
Only at very small apparent radii, $r\a \approx 0.5r_\oplus$, and only if 
secondaries host as many planets as singles and primaries, does this ``rule'' 
break down.

Of course, our model's assumptions (see the list in Sec.~\ref{sec:conclusion}) 
might not apply to the {\it Kepler}\ dataset.
However if they are applicable, then for the $56\%$ of ``\texttt{CONFIRMED}'' 
KOIs\footnote{Exoplanet Archive; \cite{akeson_nasa_2013}; 
    \url{exoplanetarchive.ipac.caltech.edu}} with 
apparent radii $>2r_\oplus$, 
whenever high-resolution imaging 
discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.

\paragraph{Fraction of detected planets with binary companions vs. apparent 
radius}
One further prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of 
detected planets with binary companions increases by $\approx 6-12\%$ going 
from $2r_\oplus$ to $\approx\! 1.4r_\oplus$.
In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
they reported the fraction of planet-hosting stars with Robo-AO detected 
companion stars, binning by Earths ($r\a < 1.6r_\oplus$), Neptunes 
($1.6r_\oplus < r\a < 3.9 r_\oplus$), Saturns ($3.9r_\oplus < r\a < 9 
r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
The reported nearby star rates and their $1\sigma$ uncertainties are:
\begin{itemize}
    \item Earths: $16.3 \pm 1.0\%$, from 1480 systems.
    \item Neptunes: $13.0 \pm 0.8\%$, from 2058 systems.
    \item Saturns: $13.6 \pm 2.0\%$, from 338 systems.
    \item Jupiters: $19.0 \pm 2.8\%$, from 247 systems.
\end{itemize} 
where the uncertainties were calculated 
following~\citet{burgasser_binarity_2003}.
The absolute values of the rates are less than the $\sim\! 45\%$ typical for 
Sun-like stars at least in part because of Robo-AO's sensitivity 
(\citealt{ziegler_robo-ao_2017}'s Fig.~2;~\citealt{raghavan_survey_2010}).
Another reason for the lower measured companion rates could be that planetary 
systems are less likely to have 
binary companions (as~\citealt{kraus_impact_2016} argued for close binary 
companions).
The uptick in the companion rate for Jupiters is likely tied to a large 
astrophysical false positive rate~\citep{santerne_sophie_2012}.
Going from Neptunes to Earths, the data suggest a weak increase in the 
detected planet companion fraction, perhaps of a few percent.
It will be interesting to see whether this effect is borne out by further 
observations.

@@

\newpage
\appendix
\section{Derivation of general formula for apparent occurrence rate}
\label{sec:appendix}

In this appendix, we derive Eq.~\ref{eq:general_Gamma_a}.
First, recall our definition of apparent rate density 
(Eq.~\ref{eq:defn_apparent_rate_density}).
Let us explicitly write $\pp=r$ and $\ps=M$; $R$ and $L$ are uniquely 
determined from the assumed stellar mass--radius--luminosity relation. We 
neglect the dependence on planetary orbital period.
The planets with $(r\a, M\a)$ are associated with 
systems of many different planetary and stellar properties, so $n_{\rm 
det}(r\a, M\a)$ is given by the convolution of the true rate density, 
$\Gamma(r, M)$, and $\mathcal{N}(r\a, M\a; r, M)$, the number (per 
unit $(r\a, M\a)$) of searchable stars that give $(r\a, M\a)$  when 
the true system actually has $(r, M)$. Mathematically,
\begin{align}
n_{\rm det}(r_a, M_a) &=
\sum_i n_{\rm det}^i(r_a, M_a) \\
&=
\sum_i \int \mathrm{d}r \mathrm{d}M \,
\mathcal{N}_{\rm s}^i(r_a,M_a; r,M)
\cdot\Gamma_i(r,M) \cdot p_{\rm tra}(r,M),
\label{eq:n_det}
\end{align}
where $i$ specifies the type of true host stars (0: single, 1: primary, 2: 
secondary).
The problem reduces to the evaluation of
\begin{equation}
\mathcal{N}_{\rm s}^i(\pp\a,\ps\a; \pp, \ps)
\end{equation}
for planets around single stars, primaries in binaries, and secondaries in 
binaries.
